\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-06-09 eg6-letters/NIM/EG6_RTPC_NIM.tex
Implement remark from Howard F.

In this paper we report the design, calibration, and performance of the radial 
TPC, organized as follows. In section \ref{sec_design}, we detail the design 
and internal structure of the detector. Section \ref{sec_readout} describes 
the properties of the read-out system. Calibration 
strategies are discussed in section \ref{sec_calib}. Finally, the performances
of the RTPC are described in section \ref{sec_perfor}.

@@

The RTPC electron collection system has 3200 readout pads. These elements are
located at the end of the amplification region, 69 mm from the central axis.
Figure \ref{fig:PADs} shows a schematic drawing of the size and 
configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in 
width.  The shift between the rows allows to reduce aliasing. Each half of the 
RTPC has 40 rows and 40 columns of pads. The shaded region in figure~\ref{fig:PADs} 
shows how pads are grouped to 16 channels pre-amplifiers. The pre-amplifier boards, 
already employed in the BoNuS RTPC \cite{BONUS-NIM}, serve the dual purpose of 
inverting the RTPC signals polarity -- from negative to positive -- to match the 
requirements of the subsequent readout system, and driving the 6~m long ribbon 
cable that connects to it.

@@

The previous discussions have shown that the two modules of the RTPC have 
slightly different behavior and give also different particle yield. However, 
this should not necessarily be linked to a different performance of the RTPC. 
Indeed, there is a complicated convolution of CLAS and the RTPC acceptances 
that can significantly affect the yields and the kinematic of the detected 
particles. To clarify this question, we measured the 
efficiency of the RTPC using the elastic scattering on $^4$He, by comparing the 
 the inclusive yield based on electron detection only to the exclusive elastic 
yield where we also detect the Helium recoil. We present in 
Figure~\ref{fig:rtpc_eff} the results for the two modules 
of the detector. We observe that the left and 
the right modules have similar efficiencies except near the target windows, as 
shown in figure \ref{fig:rtpc_eff}.

>>>>

The original design of the RTPC~\cite{BONUS-NIM} was developed for the BoNuS 
experiment at Jefferson Lab which took data in CLAS in 2005. An enhanced design 
for use in the 2009 DVCS experiment is described in section \ref{sec_design} 
of this paper. Significant improvements were made to the RTPC mechanical 
structure and fabrication technique that both increased the acceptance and 
reduced the amount of material in the path of the outgoing particles. The 
data acquisition system described in section \ref{sec_readout} was reconfigured 
to increase the event readout rate. The calibration strategy and results for 
the RTPC are discussed in section \ref{sec_calib}. Finally, the performances
of the RTPC are described in section \ref{sec_perfor}.

@@

The RTPC electron collection system has 3200 readout pads. These elements are
located at the end of the amplification region, 69 mm from the central axis.
Figure \ref{fig:PADs} shows a schematic drawing of the size and 
configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in 
width.  The shift between the rows allows to reduce aliasing. Each half of the 
RTPC has 40 rows and 40 columns of pads. The shaded region in figure~\ref{fig:PADs} 
shows how pads are grouped to 16 channels pre-amplifiers. The pre-amplifier boards, 
already employed in the BoNuS RTPC~\cite{BONUS-NIM}, serve the dual purpose of 
inverting the RTPC signals polarity -- from negative to positive -- to match the 
requirements of the subsequent readout system, and driving the 6~m long ribbon 
cable that connects to it.

@@

The previous discussions have shown that the two modules of the RTPC have 
slightly different behavior and give also different particle yield. However, 
this should not necessarily be linked to a different performance of the RTPC. 
Indeed, there is a complicated convolution of CLAS and the RTPC acceptances 
that can significantly affect the yields and the kinematic of the detected 
particles. To clarify this question, we measured the 
efficiency of the RTPC using the elastic scattering on $^4$He, by comparing the 
 the inclusive yield based on electron detection only to the exclusive elastic 
yield where we also detect the Helium recoil. We present in 
Figure~\ref{fig:rtpc_eff} the results for the two modules 
of the detector. We observe that the left and 
the right modules have similar efficiencies except near the target windows.
